Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-10-16 paper/main.tex
add plots to latex

Fig.~\ref{fig:lop_synth}: LOP syntéticas, todas en una gráfica.

>>>>

Ekhine: How many runs do we do? 10 20?

To better understand the behaviour of the algorithms, we record the fitness of
the solution evaluated at each step of each run and we average those values
over X runs on the same problem instances.  As an example, Fig.~\ref{fig:kra32}
shows the mean fitness of the solutions evaluated by uMM and CEGO on one QAP
instance. The shaded area shows one standard deviation around the
mean. Ideally, each solution evaluated helps to refine the model and leads to a
better solution being evaluated in the next step.  However, the plot shows that
the fitness of the solutions does not improve monotonically and new solutions
are often worse than their predecessors. Nevertheless, in this example, there
is a clear overall improvement as more evaluations are performed. The minimum
values achieved in the plot up to a particular number of function evaluations
gives an estimation of the mean fitness of the best-so-far solution up to that
point in the run. The algorithms do not return the final solution shown but
rather the best one (minimum fitness) of each run.

When we compare the behaviour of CEGO and uMM on synthetic LOP instances (Fig.~\ref{fig:lop_synth}).

 we 
: LOP syntéticas, todas en una gráfica.
